---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggfp

<!-- badges: start -->
<!-- badges: end -->

The goal of `ggfp` is to simplify the process of drawing forest plots using ggplot2. We have packaged the main code for drawing forest plots to form the `gg_fp()` function. `gg_fp()` has the advantage that only a few parameters need to be provided to draw a nice forest plot. Of course, it also has the obvious disadvantage that some of the more fine-grained graph adjustment parameters are not available in `gg_fp()`.

## Installation

You can install the development version of ggfp like so:

``` {r}
# devtools::install_github('lizhiwei1994/ggfp)
```

## Example

First, we create a fake data.frame to show how to use `gg_fp()`.

```{r, warning = F}
library(tidyverse)
set.seed(123)
people_name = paste('author', 1:7)
group = paste('group', 1:4)
facet = paste('facet', 1:5)

df = 
  expand.grid(people_name = people_name, 
                 group       = group,
                 facet       = facet) %>% 
  mutate(b  = rnorm(nrow(.)),
         se = rnorm(nrow(.)),
         low_95 = b - 1.96*se,
         up_95  = b + 1.96*se) %>% 
  as_tibble()

```


This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggfp)
## basic example code

gg_fp(
  data = df,
  x_axis = people_name,
  point = b,
  low = low_95,
  up = up_95,
  group_var = group,
  facet_var = facet,
  facet_color = c(rep('white', 5)),
  group_color = c('red', 'green', 'yellow', 'orange'),
  point_shape = c(16, 16, 16, 16)
  
)
```

You can change the facet strip color by giving color name to `facet_color`.


```{r change facet color}
gg_fp(
  data = df,
  x_axis = people_name,
  point = b,
  low = low_95,
  up = up_95,
  group_var = group,
  facet_var = facet,
  facet_color = c('blue', 'red', 'purple', 'blue', 'red'),
  group_color = c('red', 'green', 'yellow', 'orange'),
  point_shape = c(16, 16, 16, 16)
  
)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
